Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Text wrapping and space between citation

From these results, we recommend that physical model tests of cross-flow turbines
be performed at $Re_D \sim 10^6$ or greater to provide reasonable predictions of
full-scale performance. This threshold also applies to the validation of
predictive engineering models, especially for high-fidelity CFD models where the
boundary layer is to be resolved, since transition to turbulence plays an
important role in overall blade loading. Note that in our case, blockage, though
reasonably low, may be increasing flow through the turbine compared to a free
case, which could mean $Re$ thresholds for free flows could be slightly higher,
though a reliable blockage correction algorithm has not yet been agreed upon for
CFTs~ \cite{Cavagnaro2014}.

>>>>

From these results, we recommend that physical model tests of cross-flow
turbines be performed at $Re_D \sim 10^6$ or greater to provide reasonable
predictions of full-scale performance. This threshold also applies to the
validation of predictive engineering models, especially for high-fidelity CFD
models where the boundary layer is to be resolved, since transition to
turbulence plays an important role in overall blade loading. Note that in our
case, blockage, though reasonably low, may be increasing flow through the
turbine compared to a free case, which could mean $Re$ thresholds for free flows
could be slightly higher, though a reliable blockage correction algorithm has
not yet been agreed upon for CFTs~\cite{Cavagnaro2014}.
